\LaTeX\ Author Guidelines for ICCV Proceedings

### 2021-03-17 chapters/3_algorithm.tex
Last minor changes

\paragraph{Average, Single, and Complete Linkage} -- These three linkage criteria have been throughly studied on unsigned graphs, but never on signed graphs. In recent independent related work \cite{chehreghani2020hierarchical}, the authors prove that applying these three linkage methods to a signed graph is equivalent to applying them to the unsigned graph obtained by shifting all edge weights by a constant.  Here, we prove which of the algorithms studied here is ``intrinsically'' signed and do not have this invariance-property:
\begin{restatable}{prop}{invariantAlgs}
\label{prop:weight_shift_invariant}
We call an agglomerative algorithm ``weight-shift invariant'' if the dendrogram $T$ returned by the algorithm is invariant w.r.t. a shift of all edge weights $w_e$  by a constant $\alpha\in \mathbb{R}$. Among the variations of \algname{}, only hierarchical clustering with Average (HC-Avg), Single (HC-Single), and Complete linkage (HC-Complete) are weight-shift-invariant (see green box in Table~\ref{tab:linkage-criteria}).
\end{restatable}
\noindent To our knowledge, Average and Single linkage methods have never been combined with cannot-link constraints on signed graphs, so we name these algorithms \emph{HCC-Avg} and \emph{HCC-Single}. On the other hand, we prove that an agglomerative algorithm with Complete linkage (HC-Complete) returns the same clustering whether cannot-link-constraints are enforced or not (Lemma \ref{lemma:absMax_and_complete_property}, in Appendix).
% , we prove that with Complete linkage the agglomeration order does not change whether constraints are introduced or not.

@@

\paragraph{Algorithms defining an ultrametric} -- The connection between agglomerative algorithms and ultrametrics\footnote{A metric space $(X,d)$ is an \emph{ultrametric} if for every $x,y,z \in X$, $d(x,y)\leq \max \{d(x,z), d(y,z)\}$.} is well known. Usually, ultrametrics are associated to strictly positive \emph{similarity} or \emph{dissimilarity} measures on a graph. In our framework, a trivial ultrametric is always given by the height $h_T$ of the dendrogram. However, we now prove that, similarly to what has been done for HC on unsigned graphs \cite{johnson1967hierarchical,milligan1979ultrametric}, for some of the \algname{} variations we can define an ultrametric based on the edge weights and the interactions between clusters. To define this measure, we first map the signed interaction $\treeHeight{}$ defined in Eq.~\ref{eq:def_dendr_interact} to positive ``pseudo-distances'' $d_{T}:V \times V \rightarrow \mathbb{R}^{+}$:
\begin{align}\label{eq:UM_def}
d_{T}(u,v)\equiv &\begin{cases}
0 & \text{if}\,\, u=v\\
M-\treeHeight(u,v) & \text{if}\,\, u\neq v
\end{cases}\quad \forall u,v\in V\\
\mathrm{where}& \quad  M \equiv  \epsilon + \max_{u',v'\in V,\,u'\neq v'}\treeHeight(u',v')
\end{align}
and where $\epsilon > 0$. 
% By definition, we have that $d_{T}(u,v)=d_{T}(v,u)$ and $d_{T}(u,u)= 0$. 
We then prove the following proposition:
\begin{restatable}{prop}{secondUltraMetricProperty}
\label{prop:ultraMetric2}
% Consider the binary rooted tree $T^*$ returned by the \TODO{all variants in Table 1} \algname{} Algorithm~\ref{main_alg}, given a choice of linkage criteria $\interact{}$ and the use (or not) of CannotLinkConstraints. 
Among the algorithms included in the \algname{} framework (see Table \ref{tab:linkage-criteria}), only Mutex Watershed and hierarchical clustering with Average (HC-Avg), Single (HC-Single) and Complete linkage (HC-Complete) define an ultrametric $(V, d_{T^*})$, where $d_{T^*}$ is defined in Eq.~\ref{eq:UM_def} and $T^*$ is the tree returned by the \algname{} Algorithm~\ref{main_alg}.
\end{restatable}
Now that we have defined the algorithms and characterized them from a theoretical point of view, we move to empirical evaluation in the next section.

>>>>

\paragraph{Average, Single, and Complete Linkage} -- These three linkage criteria have been thoroughly studied on unsigned graphs, but never on signed graphs. In recent independent related work \cite{chehreghani2020hierarchical}, the authors prove that applying these three linkage methods to a signed graph is equivalent to applying them to the unsigned graph obtained by shifting all edge weights by a constant.  Here, we prove which of the algorithms studied here is ``intrinsically signed'' and do not have this invariance-property:
\begin{restatable}{prop}{invariantAlgs}
\label{prop:weight_shift_invariant}
We call an agglomerative algorithm ``weight-shift invariant'' if the dendrogram $T$ returned by the algorithm is invariant w.r.t. a shift of all edge weights $w_e$  by a constant $\alpha\in \mathbb{R}$. Among the variations of \algname{}, only hierarchical clustering with Average (HC-Avg), Single (HC-Single), and Complete linkage (HC-Complete) are weight-shift-invariant (see green box in Table~\ref{tab:linkage-criteria}).
\end{restatable}
\noindent Although average and single linkage methods have been largely studied on unsigned graphs, to our knowledge, they have never been combined with cannot-link constraints on signed graphs\footnote{Note that Complete linkage methods return the same clustering whether constraints are enforced or not (proof in Lemma \ref{lemma:absMax_and_complete_property}, in Appendix).}, so we name these algorithms \emph{HCC-Avg} and \emph{HCC-Single}. 
% On the other hand, we prove that an agglomerative algorithm with Complete linkage (HC-Complete) returns the same clustering whether cannot-link-constraints are enforced or not (Lemma \ref{lemma:absMax_and_complete_property}, in Appendix).
% , we prove that with Complete linkage the agglomeration order does not change whether constraints are introduced or not.

@@

\paragraph{Algorithms defining an ultrametric} -- The connection between agglomerative algorithms and ultrametrics\footnote{A metric space $(X,d)$ is an \emph{ultrametric} if, for every $x,y,z \in X$, $d(x,y)\leq \max \{d(x,z), d(y,z)\}$.} is well known. Usually, ultrametrics are associated to strictly positive \emph{similarity} or \emph{dissimilarity} measures on a graph. In our framework, a trivial ultrametric is always given by the height $h_T$ of the dendrogram. However, for some of the \algname{} variations, we now define an ultrametric based on the edge weights and the signed interactions between clusters, generalizing what has been done for HC on unsigned graphs \cite{johnson1967hierarchical,milligan1979ultrametric}. To define this measure and prove its ultrametric property, we first map the signed interaction $\treeHeight{}$ defined in Eq.~\ref{eq:def_dendr_interact} to positive ``pseudo-distances'' $d_{T}:V \times V \rightarrow \mathbb{R}^{+}$:
\begin{align}\label{eq:UM_def}
d_{T}(u,v)\equiv &\begin{cases}
0 & \text{if}\,\, u=v\\
M-\treeHeight(u,v) & \text{if}\,\, u\neq v
\end{cases}\quad \forall u,v\in V\\
\mathrm{where}& \quad  M \equiv  \epsilon + \max_{u',v'\in V,\,u'\neq v'}\treeHeight(u',v')
\end{align}
and where $\epsilon > 0$. 
% By definition, we have that $d_{T}(u,v)=d_{T}(v,u)$ and $d_{T}(u,u)= 0$. 
We then prove the following proposition:
\begin{restatable}{prop}{secondUltraMetricProperty}
\label{prop:ultraMetric2}
% Consider the binary rooted tree $T^*$ returned by the \TODO{all variants in Table 1} \algname{} Algorithm~\ref{main_alg}, given a choice of linkage criteria $\interact{}$ and the use (or not) of CannotLinkConstraints. 
Among the algorithms included in the \algname{} framework (see Table \ref{tab:linkage-criteria}), only Mutex Watershed and hierarchical clustering with Average (HC-Avg), Single (HC-Single) and Complete linkage (HC-Complete) define an ultrametric $(V, d_{T^*})$, where $d_{T^*}$ is defined in Eq.~\ref{eq:UM_def} and $T^*$ is the tree returned by the \algname{} Algorithm~\ref{main_alg}.
\end{restatable}
Now that we have extended the family of HC algorithms \cite{johnson1967hierarchical,milligan1979ultrametric} with ``weight-based ultrametrics'' to signed graphs, we move on to their empirical evaluation.

### 2021-03-17 chapters/5_experiments_intro.tex
Last minor changes

\textbf{Scores on CREMI instance-segmentation} -- 
SSBM graphs are \emph{non-planar}, and every edge has the same probability to be present in the graph. On the other hand, the \emph{gridGraph} and \emph{3D-RAG} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: regardless of whether a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance). 
Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show that average linkage methods (HC-Avg, HCC-Avg) strongly outperform other methods on \emph{CREMI-gridGraph} instances and also achieve the best scores on \emph{CREMI-3D-rag} graphs. Sum-based linkage methods (GAEC, HCC-Sum) have a two times higher ARAND error on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}). This suggests that the \emph{flooding strategy} observed previously in the sum-linkage methods does not work on grid-graphs, because in this setup edge weights are predicted by a CNN and noise is strongly spatially-correlated \footnote{This effect is not as strong on \emph{3D-RAG} graphs, because edge weights are computed by averaging CNN predictions (and noise) over the boundaries of adjacent supervoxels.}.
To fully test this hypothesis, we conduct a set of experiments where the CNN predictions are perturbed by adding structured noise and simulating additional artifacts like ``holes'' in the boundary evidence\footnote{See Appendix \ref{sec:appendix_noise_gen} for details about how we perturbed the \emph{CREMI-gridGraph} problems by using Perlin noise \cite{perlin2001noise,perlin1985image}, which is one of the most common gradient noises used in procedural pattern generation.}. 
The plot in Fig.~\ref{fig:scores_structured_noise} confirms that HC-Avg and HCC-Avg are very robust algorihtms on this data, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (MWS). It is not a surprise that the AbsMax linkage used by MWS is not robust to this type of structured noise. However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} prove how MWS can achieve high accuracy with considerably lower runtimes.

@@

\textbf{Results on CREMI challenge} -- 
Table~\ref{tab:cremi_leaderboard} shows that the HCC-Avg and HC-Avg clustering algorithms achieve state-of-the-art accuracy on the CREMI challenge, when combined with predictions of our CNN.
Most of the other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs. As we show in Table ~\ref{tab:scores_3drag}, using super-pixels considerably reduces the size of the clustering problem and, consequently, the post-processing time. 
However, our method operating directly on pixels (\emph{gridGraph + HCC-Avg}) achieves better performances than superpixel-based methods (\emph{3D-RAG + HCC-Avg}) and does not require the parameter tuning necessary to obtain good super-pixels, which is usually highly dataset dependent.
To scale up our method operating on pixels, we divided each test-volume into four sub-blocks, and then combined the resulting clusterings by running the algorithms again on the combined graph.
The method \emph{3D-RAG + LiftedMulticut} based on the lifted multicut approximation of \cite{beier2017multicut} achieves the best scores overall, but it takes into account different information through the lifted edge weights that also depend on additional raw-data and shape information from highly engineered super-pixels. 
% Note that the test volumes of the challenge contain several imaging artifacts that make segmentation particularly challenging.
% However: handcrafted and dataset dependent, performs better, no

>>>>

\textbf{Scores on CREMI instance-segmentation} -- 
SSBM graphs are \emph{non-planar}, and every edge has the same probability to be present in the graph. On the other hand, the \emph{gridGraph} and \emph{3D-RAG} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: regardless of whether a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance). 
Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show that average linkage methods (HC-Avg, HCC-Avg) strongly outperform other methods on \emph{CREMI-gridGraph} instances and also achieve the best scores on \emph{CREMI-3D-rag} graphs. Sum-based linkage methods (GAEC, HCC-Sum) have a two times higher ARAND error on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}). This suggests that the \emph{flooding strategy} observed previously in the sum-linkage methods does not work on grid-graphs, because in this setup edge weights are predicted by a CNN and noise is strongly spatially-correlated \footnote{This effect is not as strong on \emph{3D-RAG} graphs, because edge weights are computed by averaging CNN predictions (and noise) over the boundaries of adjacent supervoxels.}.
To fully test this hypothesis, we conduct a set of experiments where the CNN predictions are perturbed by adding structured noise and simulating additional artifacts like ``holes'' in the boundary evidence\footnote{See Appendix \ref{sec:appendix_noise_gen} for details about how we perturbed the \emph{CREMI-gridGraph} problems by using Perlin noise \cite{perlin2001noise,perlin1985image}, which is one of the most common gradient noises used in procedural pattern generation.}. 
The plot in Fig.~\ref{fig:scores_structured_noise} confirms that HC-Avg and HCC-Avg are very robust algorihtms on this data, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (MWS). It is not a surprise that the AbsMax linkage used by MWS is not robust to this type of structured noise. However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} prove how MWS can achieve high accuracy with 70\% lower runtime compared to HC-Avg.

@@

\textbf{Results on CREMI challenge} -- 
Table~\ref{tab:cremi_leaderboard} shows that the HCC-Avg and HC-Avg clustering algorithms achieve state-of-the-art accuracy on the CREMI challenge, when combined with predictions of our CNN.
Most of the other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs. As we show in Table ~\ref{tab:scores_3drag}, using superpixels considerably reduces the size of the clustering problem and, consequently, the post-processing time. 
However, our method operating directly on pixels (\emph{gridGraph + HCC-Avg}) achieves better performances than superpixel-based methods (\emph{3D-RAG + HCC-Avg}) and does not require the parameter tuning necessary to obtain good super-pixels, which is usually highly dataset dependent.
To scale up our method operating on pixels, we divided each test-volume into four sub-blocks, and then combined the resulting clusterings by running the algorithms again on the combined graph.
The method \emph{3D-RAG + LiftedMulticut} based on the lifted multicut approximation of \cite{beier2017multicut} achieves the best scores overall, but it takes into account different information through the lifted edge weights that also depend on additional raw-data and shape information from highly engineered super-pixels. 
% Note that the test volumes of the challenge contain several imaging artifacts that make segmentation particularly challenging.
% However: handcrafted and dataset dependent, performs better, no
